Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-13 paper/paper.tex

Formally, the online \emph{Balanced RePartitioning} problem (\OBRP{}) is defined as
follows. We are given a set of $n$ nodes,
initially arbitrarily partitioned into $\ell$~clusters,
each of size~$k$.
We say that nodes in $C \subset V$ are \emph{collocated} in a partition $P$
if they are assigned to the same cluster.
%\maciek{We can ommit the formal definition: "I.e.,
%$\forall u,v \in C: \mathit{cluster} (u,P) = \mathit{cluster} (v,P)$.". %However, if we use the notion of cluster later, then TODO: define cluster}
The input consists of a sequence of pairwise communication requests
$\sigma = (u_1,v_1),$ $(u_2,v_2),$ $(u_3,v_3), \ldots$,
where a pair $(u_t,v_t)$ indicates that nodes $u_t$ and $v_t$ exchange a fixed amount of data.
Before serving the request,
the online algorithm
can re-partition,
i.e.,
it may (optionally) move some of the nodes into clusters different than their current assigned clusters.
Once the re-partition is executed,
we serve
the communication request between two  nodes at cost~0 if they are collocated,
or at cost~1 if they are located in different clusters.
The cost of migrating a node from one cluster to another
is~$\alpha \in \mathbb{Z}^+$.
For any algorithm $ALG$,
its cost,
denoted by $ALG(\sigma)$,
is the total cost of communications and
the cost of migrations performed by $ALG$ while serving the sequence $\sigma$.

\maciek{Here introduce a restricted model of \PPOBRP{}, the restricted variant where the input sequence can be perfectly partitioned}
\maciek{ every algorithm must colocate every communicating pair.}

>>>>

Formally, the online \emph{Balanced RePartitioning} problem (\OBRP{}) is defined as
follows. We are given a set of $n$ nodes,
initially arbitrarily partitioned into $\ell$~clusters,
each of size~$k$.
We say that nodes in $C \subset V$ are \emph{collocated} in a partition $P$
if they are assigned to the same cluster.
%\maciek{We can ommit the formal definition: "I.e.,
%$\forall u,v \in C: \mathit{cluster} (u,P) = \mathit{cluster} (v,P)$.". %However, if we use the notion of cluster later, then TODO: define cluster}
%\maciek{We can ommit the formal definition: "I.e.,
%$\forall u,v \in C: \mathit{cluster} (u,P) = \mathit{cluster} (v,P)$.". However, if we use the notion of cluster later, then TODO: define cluster}
The input consists of a sequence of pairwise communication requests
$\sigma = (u_1,v_1),$ $(u_2,v_2),$ $(u_3,v_3), \ldots$,
where a pair $(u_t,v_t)$ indicates that nodes $u_t$ and $v_t$ exchange a fixed amount of data.
Before serving the request,
the online algorithm
can re-partition,
i.e.,
it may (optionally) move some of the nodes into clusters different than their current assigned clusters.
Once the re-partition is executed,
we serve
the communication request between two  nodes at cost~0 if they are collocated,
or at cost~1 if they are located in different clusters.
The cost of migrating a node from one cluster to another
is~$\alpha \in \mathbb{Z}^+$.
For any algorithm $ALG$,
its cost,
denoted by $ALG(\sigma)$,
is the total cost of communications and
the cost of migrations performed by $ALG$ while serving the sequence $\sigma$.

\subsection{Perfect Partition Model}\label{sec:perfectPartition}
\maciek{Here introduce a restricted model of \PPOBRP{}, the restricted variant where the input sequence can be perfectly partitioned}
\maciek{ every algorithm must colocate every communicating pair.}

In this paper we mostly focus on a restricted variant of   \PPOBRP{}
where the communication graph can be partitioned into $\ell$ clusters without any inter-cluster edges.
Moreover, we assume an optimal offline algorithm (OPT) moves to this \emph{perfect partition}
at the beginning and stays there permanently.
Then the task of an online algorithm is to "recover" (or learn) the perfect partition while not paying too much more than OPT.
